HPC--101 -- Cheatsheet \vspace{-2ex}

### 2016-01-22 hpc_101/cheatsheet/paper.tex
minor tweeks

\section{SSH/SCP}
\begin{itemize}
\item \texttt{ssh {\lft}user{\rht}@{\lft}host{\rht}}
\item \texttt{ssh -Y {\lft}user{\rht}@{\lft}host{\rht}}\desc{Enable X11 forwarding}
\item \texttt{scp~{\lft}file{\rht}~{\lft}user{\rht}@{\lft}host{\rht}:{\lft}remote~path{\rht}}\desc{Copy a file to a remote location}
\item \texttt{scp~-r~{\lft}dir{\rht}~{\lft}user{\rht}@{\lft}host{\rht}:{\lft}remote~path{\rht}}\desc{Recursivly copy a directory to a remote location}
\end{itemize}

\section{SLURM}
\subsection{Management And Monitoring}
\begin{itemize}
\item[] \texttt{sbatch \pth{slurm\_script}}\desc{Submit a slurm script to the scheduler for batch processing}
\item[] \texttt{sbatch~--array=[\#-\#]~\pth{slurm\_script}}\desc{Submit a job array to the scheduler}
\item[] \texttt{srun} \desc{Used in submitting an interactive job, or also  used within a slurm\_script}
\item[] \texttt{srun.x11} \desc{Used in submitting an interactive job, that also forwards the X, if you logged in while enabling X forwarding}
\item{} \texttt{squeue} \desc{Display all jobs running or waiting on the cluster}
\item{} \texttt{squeue -u{\lft}user{\rht}} \desc{Only display jobs for the specified user}
\item{} \texttt{sinfo} \desc{Display the partitions and nodes state}
\item{} \texttt{scancel {\lft}jobid{\rht}} \desc{Cancel the specified job}
\end{itemize}

\subsection{Details and Profiling}
\begin{itemize}
\item[] \texttt{scontrol show jobid {\lft}jobid{\rht}}\desc{Show job details of a waiting or running job}
\item[] \texttt{scontrol show parition {\lft}partition name{\rht}}\desc{Show details of the specified partition}
\item[] \texttt{scontrol show node {\lft}node name{\rht}}\desc{Show details of the specified node}
\item[] \texttt{sacct -l -j {\lft}jobid{\rht}}\desc{Show usage details of a job}
\item[] \texttt{sacct -u {\lft}user{\rht}}\desc{Show all jobs from a given user}
\end{itemize}

@@

\subsection{Globus Endpoints}
\begin{itemize}
\item[] login-0001 -- \texttt{hawaii#UHHPC1}
\item[] login-0002 -- \texttt{hawaii#UHHPC2}
\end{itemize}

>>>>

\section{SSH/SCP}
\begin{itemize}
\item[] \texttt{ssh {\lft}user{\rht}@{\lft}host{\rht}}
\item[] \texttt{ssh -Y {\lft}user{\rht}@{\lft}host{\rht}}\desc{Enable X11 forwarding}
\item[] \texttt{scp~{\lft}file{\rht}~{\lft}user{\rht}@{\lft}host{\rht}:{\lft}remote~path{\rht}}\desc{Copy a file to a remote location}
\item[] \texttt{scp~-r~{\lft}dir{\rht}~{\lft}user{\rht}@{\lft}host{\rht}:{\lft}remote~path{\rht}}\desc{Recursivly copy a directory to a remote location}
\end{itemize}

\section{SLURM}
\subsection{Management And Monitoring}
\begin{itemize}
\item[] \texttt{sbatch \pth{slurm\_script}}\desc{Submit a slurm script to the scheduler for batch processing}
\item[] \texttt{sbatch~--array=[\#-\#]~\pth{slurm\_script}}\desc{Submit a job array to the scheduler}
\item[] \texttt{srun} \desc{Used in submitting an interactive job, or also  used within a slurm\_script}
\item[] \texttt{srun.x11} \desc{Used in submitting an interactive job, that also forwards the X, if you logged in while enabling X forwarding}
\item[] \texttt{squeue} \desc{Display all jobs running or waiting on the cluster}
\item[] \texttt{squeue -u{\lft}user{\rht}} \desc{Only display jobs for the specified user}
\item[]\texttt{sinfo} \desc{Display the partitions and nodes state}
\item[] \texttt{scancel {\lft}jobid{\rht}} \desc{Cancel the specified job}
\end{itemize}

\subsection{Details and Profiling}
\begin{itemize}
\item[] \texttt{scontrol show jobid {\lft}jobid{\rht}}\desc{Show job details of a waiting or running job}
\item[] \texttt{scontrol show parition {\lft}partition{\rht}}\desc{Show details of the specified partition}
\item[] \texttt{scontrol show node {\lft}node name{\rht}}\desc{Show details of the specified node}
\item[] \texttt{sacct -l -j {\lft}jobid{\rht}}\desc{Show usage details of a job}
\item[] \texttt{sacct -u {\lft}user{\rht}}\desc{Show all jobs from a given user}
\end{itemize}

@@

\subsection{Globus Endpoints}
\begin{itemize}
\item[] login-0001 -- \texttt{hawaii\#UHHPC1}
\item[] login-0002 -- \texttt{hawaii\#UHHPC2}
\end{itemize}
